Distributed recycling for additive manufacturing: an ecosystem services perspective 

### 2021-09-14 00-ES/Article/Draft.Rmd
version beta sent to Nadege

---
title: "Distributed recycling for additive manufacturing: an ecosystem services perspective "
documentclass: extarticle
fontsize: 14pt
#geometry: "left=3cm, right=2cm,top=2.5cm,bottom=2cm"
output: 
  bookdown::pdf_document2:
    toc: false
  #   keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
# abstract
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
#options(tinytex.engine_args = '--shell-escape')

@@

<!-- DRAM -->
Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
However, as with any recycling system, its feasibility must be evaluated before its implementation. Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain. Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory. 
The purpose of this research is to identify the the set of principles, criteria and indicators from ecosystem services framework, that can be associated to distributed recycling approach, evaluating their pertinence in the local impact in terms of availability of data. 
The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.

This study seeks to address the following questions: 
- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?

While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
Main tasks in this research include a systematic literature review of ecosystem services in recycling field, and the creation of a database and online tool to map these element in the local territory.

# Background

<!--# Intro -->
Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2009]. 
Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@ref].
Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].

@@

<!--# Classification of ES -->
Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
The Economics of Ecosystems and BiodiversityTBB [@ref],
THe Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES) . 
In the heart of the four main, they share four main categories of ES:
**Provisioning** (e.g. food and medicines); 
**Regulating** (e.g. pollination and climate regulation), 
**Supporting** (e.g soil formation and fixation of solar energy) and 
**Cultural / Information** services (e.g. artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].

@@

  <!-- CICES -->
The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref]. 
In CICES framework, @Potschin argued the conceptual framework of cascading aspect from ecosystesm service tos of the and are commonly divided into 
@Mustajoki2019

@@

CICES %>% flextable() %>%
  set_caption("CICES ") %>%
  #autofit() %>% 
  width(j=1:5, width = c(1, 1, 2, 2, 2)) %>% 
  fontsize(size=10, part = "all") %>% 
  #fit_to_width(max_width = 8) %>% 
  merge_v(j = c("Section", "Division",  "Class type")) %>% #"Group", "Class",
  theme_booktabs()

@@

<!--  Research themes in ES -->
Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field. Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.

<!-- Importance of ES in the decision making process -->
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers. It is difficult to provide information about pressure from industrial systems in corporate information systems. EE uses valuation techniques to reveal the value of nature and develops ways to overcome the current technical and ethical challenges to valuation, for example, by broadening the dominant monetary perspective on the value of nature by nonmonetary and deliberative approaches influence decision makers.

- Hoy en dia es necesario tener en cuenta no solo un factor technic-econonomic en el momento de evaluar soluciones en amount. Tambien, es necesario estavlecer cuales serain las implicationes y los impactos para el territoirio desde el punto de vista de servicios ecosistemicos

@@

<!-- Importance of ES in the Engineering -->
The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
  <!-- Engineering blindness -->
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal. This scenario is not true today.
  <!-- Engineering withing ecological constraints -->
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@ref].
  <!-- MEA and Planeatry results -->
According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
  <!-- Causas of exceeding Planeatry boundaries -->
Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions [@Liu2019g].
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
<!-- Purpose of strong sustainability -->
Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016]. 
  <!-- Expand boundaries of Engineering -->
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].

<!-- Sustainability frameworks -->
@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level. 
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
<!-- They hightligthed that differens Systemic design approaches are   -->
  <!-- TES -->
@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
This theoretical framework aims to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g. for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

relies on the idea of TES and develops ways of enhancing synergies between a local scale manufacturing process and the land around it.

The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing. 
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not

@@

Four major steps are proposed as illustrated in figure XX .

  <!-- Step 1 Assessments-->
The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
  <!-- Step 2 Plannig-->
In the *Assessment* step, the main aim is to jeopordize the key ecosystems services and the respective scales that are going to be included in the analysis. 
These elements will be a intersection of the technological and geographihcal issues based on a analysis of each systems.
  <!-- Step 3 Evaluate-->
In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
  <!-- Step 3 Management-->
Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.

```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht'}

@@

@@

It is needed to define two types of scopes: technological and ecological.

@@

Terminology %>% flextable() %>%
  set_caption("Terminology used in the deifnition of the spheres") %>%
  width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
  theme_booktabs() %>% 
  hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
  padding(padding = 0)

@@

@@

<!-- Technological -->
Regarding the technological sphere, three scales are analysed: *Equipment*, *Value chain* and *Economy* scales.
  <!-- Equipment -->
The technological system at the equipment scale is represented as $T_{i,j}$ which consists of the *i-th* facility for the *j-th* technological activity. 
For example, in the case of a specific technological activity ($j = 1$) such as corn farming, $T_{1,1}$ and $T_{1,1}$ represent two different facilities or farms for this activity. 
  <!-- Value chain -->
Technological systems at the value chain scale are indicated as $\underline{T_{j}}$.
These represent average value chain activities within a region, whose information is generally available from inventory databases.
  <!-- Economy -->
Technological systems at the economy scale are represented as $\doverline{T_{j}}$.
These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.

@@

@Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
It represents the total amount of ES needed to  mitigate the emission or atisfy the resource use?
For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.

@@

<!-- Intro to problem of LCA -->
Usually, Life cycle analysis  do not integrate explicitaly models and data about ecosystem goods and services [@ref]
Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.

@@

<!-- Establish ecological models -->
There is a research efforts to establish the knowledge about the supply of ES using ecological models such as 
  <!-- Ecological models -->
i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas (USEPA

- to complete the different odels for each ES?
- More references on this

@@

###Impact Assessment

In this step, the echno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
For the k-th ES, the sustainability metric $V_{k}$ is:

@@

###
## Management

>>>>

---
title: "Distributed recycling for additive manufacturing: an ecosystem services perspective "
documentclass: extarticle
fontsize: 14pt
geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
output: 
  bookdown::pdf_document2:
    toc: true
    keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
# abstract
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
  \usepackage{tabu}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%')
options(knitr.kable.NA = '')
#options(tinytex.engine_args = '--shell-escape')

@@

<!-- Intro -->
The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
No country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.

<!-- Gap in the literature -->
However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems. 
This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements. 
  <!-- Case study -->
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
Therefore, new approaches need to be explored in order to reduce ar at least recycling this material. 
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

The expected results seek to address the following questions:

- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory? 
From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators   for deployments distributed recycling approach,

In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.

\textcolor{red}{The article is structure as follows.... ( to complete) } section \@ref(background) ...

<!-- The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.  -->

# Background
\label{background}

## Ecosystem services

<!--# Intro -->
Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002]. 
Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].

@@

<!--  Research themes in ES -->
Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field. 
Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.

<!--# Classification of ES -->
Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
In the heart of the four main, they share four main categories of ES:
**Provisioning** (e.g. food and medicines); 
**Regulating** (e.g. pollination and climate regulation), 
**Supporting** (e.g soil formation and fixation of solar energy) and 
**Cultural / Information** services (e.g. artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].

```{r Fig:ES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
# img_url <- paste0(URL, 'Everest-bio/ES')
#download.file(paste0(URL, 'Everest-bio/ES/', 'Comparison.png'), "Figures/Comparison.png")
# rsvg_pdf(img_url, "Figures/Methodology.pdf")

knitr::include_graphics('Figures/Comparison.png')

@@

  <!-- CICES -->
The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref]. 
In CICES framework, @Potschin-Young2018 argued the conceptual framework of cascading aspect from ecosystesm service are  commonly divided Groups, division.
<!-- @Mustajoki2019 -->

@@

CICES %>% pull(Section) 
names(CICES)
CICES %>% flextable() %>%
  set_caption("CICES ") %>%
  #autofit() %>% 
  width(j=1:5, width = c(1, 1, 2, 2, 2)) %>% 
  fontsize(size=10, part = "all") %>% 
  #fit_to_width(max_width = 8) %>% 
  merge_v(j = c("Section", "Division",  "Class type")) %>% #"Group", "Class",
  theme_booktabs()

@@

```{r Fig-ES-cices, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
# img_url <- paste0(URL, 'Everest-bio/ES')
# rsvg_pdf(img_url, "Figures/Methodology.pdf")

knitr::include_graphics('Figures/cices.png')

\textcolor{red}{to complete ... }

## Distributed recycling via additive manufacturing

<!-- DRAM -->
Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management [@CruzSanchez2020; @Santander2020]. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

\textcolor{red}{ To complete ...}

@@

<!-- Importance of ES in the Engineering -->
The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
  <!-- Engineering blindness -->
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal. This scenario is not true today.
  <!-- Engineering withing ecological constraints -->
 The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
 <!-- Importance of ES in the decision making process -->
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
It is difficult to provide information about pressure from industrial systems in corporate information systems. 
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@ref].

  <!-- MEA and Planeatry results -->
According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
  <!-- Causas of exceeding Planeatry boundaries -->
Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions [@Liu2019g].
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
<!-- Purpose of strong sustainability -->
Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016]. 
  <!-- Expand boundaries of Engineering -->
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].

<!-- Sustainability frameworks -->
@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level. 
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
<!-- They hightligthed that differens Systemic design approaches are   -->
  <!-- TES -->
@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g. for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017]. -->
<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.  -->

\textcolor{red}{
Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}

@@

```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht', fig.align='center'}

@@

Four major steps are proposed as illustrated in figure \@ref(Fig-Methodology) .

  <!-- Step 1 Assessments-->
The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
  <!-- Step 2 Plannig-->
In the *Assessment* step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis. 
These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
  <!-- Step 3 Evaluate-->
In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
  <!-- Step 3 Management-->
Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.

@@

Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.

@@

set_flextable_defaults(
  padding = 0,
  line_spacing = 1,
  border.color = '#000000'
)
Terminology %>% flextable() %>%
  set_caption("Terminology used in the deifnition of the spheres") %>%
  width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
  # theme_booktabs() %>% 
  hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
  #border(border.top = officer::fp_border(color = "black") ) %>% 
  padding(padding = 0)

@@

```{r Fig-spheres, fig.cap='Notation for assessing techno-ecological synergies', out.width='100%', fig.pos='!ht'}

# img_url <- paste0(URL, 'Everest-bio/Systemes.svg')
# rsvg_pdf(img_url, "Figures/Systemes.pdf")

knitr::include_graphics('Figures/Systemes.pdf')
```

### Territorial issues

\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}

### Industrial Issues

\textcolor{red}{ To complete based on article that reading on...}

@@

It is needed to define two types of scopes: technological and ecological.
<!-- Technological -->
Regarding the technological sphere, three scales are analysed: *Equipment*, *Value chain* and *Economy* scales.
  <!-- Equipment -->
The technological system at the equipment scale is represented as $T_{i,j}$ which consists of the *i-th* facility for the *j-th* technological activity. 
For example, in the case of a specific technological activity ($j = 1$) such as corn farming, $T_{1,1}$ and $T_{1,1}$ represent two different facilities or farms for this activity. 
  <!-- Value chain -->
Technological systems at the value chain scale are indicated as $\underline{T_{j}}$.
These represent average value chain activities within a region, whose information is generally available from inventory databases.
  <!-- Economy -->
Technological systems at the economy scale are represented as $\overline{T_{j}}$.
These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.

@@

@Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
It represents the total amount of ES needed to  mitigate the emission or satisfy the resource use.
For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.

@@

<!-- Intro to problem of LCA -->
Usually, Life cycle analysis  do not integrate explicitly models and data about ecosystem goods and services [@ref]
Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.

@@

<!-- Establish ecological models -->
There is a research efforts to establish the knowledge about the supply of ES using ecological models such as 
  <!-- Ecological models -->
i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..

\textcolor{red}{to complete ... }

1. to complete the different models for each ES?.
2. More references on this

@@

### Techno-ecological synergy

In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
For the k-th ES, the sustainability metric $V_{k}$ is:

@@

## Management

### Interpretation

A hierarchy of metrics 
The Techno-Ecological Synergy (TES) metric obtained are multi-scale and multidimensional.
Therefore, these metrics  may be interprested by plotting the local and servicehed scale metrics.

```{r Fig:Quandrantes, out.width='100%'}
# img_url <- paste0(URL, 'Everest-bio/Quadrantes-sustainability.svg')
# rsvg_pdf(img_url, "Figures/Quadrantes-sustainability.pdf")

knitr::include_graphics('Figures/Quadrantes-sustainability.pdf')
```

Figure \@ref(Figure-TES) present four quadrants that represent the sustainability.
  <!-- Quadrant I -->
Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed’s ecological capacity. 
From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
  <!-- Quadrant III -->
On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
Ecological overshoot exists at both local and serviceshed scales. 
Efforts toward improvement should reduce emissions and restore ecosystems at both

Regarding the quandrant II, it represents the situation where the ES is used sustainably in the serviceshed but not at the local scale. 
This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand. 
Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support [@ref]. 
On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed. 
Here, the activity is an “island of sustainability” [@Wallner1996].
If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.

### Improvements and Design in the system

  <!-- Goal of the step -->
In this step, the main goal is to put effort for making changes such that $V_{i,j,k} \geq 0, \forall\{i,j,k\}$.
This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services. 
This final vision is to encourage engineering and human activities to be within ecological constraints.

Three main elements in terms of design is expected in this step
The first is the explicit recognition of the inherent interdependencies between technological and ecological systems. 
Such recognition enables a better understanding of the resiliency of coupled techno-ecological systems during any enhancement of technological efficiency or restoration of ecological service provision. 
The collaboration with multi-stakeholders is expected in this step.

Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process. 
If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for $V\{i,j,k\} \geq 0$ for some values of $i, j,$ and $k$. 
Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc. 
For such molecules, the only way to satisfy the TES objective of $V\{i,j,k\} \geq 0$ is by technological changes. 
One approach is to treat such molecules as "technological nutrients" and like biological nutrients, to recycle in technological systems.
Nonrenewable resources will invariably result in values of $V\{i,j,k\} \geq 0$. 
Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.

### Establishment on Scenarios

\textcolor{red}{to complete ... }
